\plaintitle

### 2016-09-21 drafts/labor/complexity.tex

\subsubsection{\implication}
% \topic{The piecework literature gives us a template for pushing the boundaries of complexity in piecework, but
% it also signals some of the ultimate limitations of crowd work and piecework in general.}
% While the threshold preventing task requesters from utilizing piecework
% has dropped thanks to affordances of the Internet, the ceiling on task complexity hasn't moved significantly.
% \msb{is that your prediction? I would argue against the fact that it hasn't moved significantly, crowdforge did far more complex work, as did flash teams and flash orgs}
% If we're to make use of \citeauthor{Brown01041990}'s prescriptions,
% we would benefit from finding ways to decompose varied tasks into homogeneous microtasks. \msb{isn't that what we've been doing all along?}
Technology's ability to support human cognition will enable stronger assumptions about workers' abilities, increasing the complexity of crowd work outcomes much like the shift to expert crowdsourcing.
Further improvements would most likely come from replicating the success of narrowly-slicing education for expert work as \citeauthor{hart2013rise} and \citeauthor{grier2013computers} described in their piecework examples
of human computation \cite{grier2013computers} and drastically reformulating macro--tasks given the constraints of piecework \cite{hart2013rise}.
To some extent, an argument can be made that
MOOCs and other online education resources
provide crowd workers with the resources that they need, but 
it remains to be seen whether that work will be appropriately valued, let alone
properly interpreted by task solicitors
\cite{aguaded2013mooc}.
If we can overcome this obstacle,
we might be able to empower more crowd workers to do complex work such as engineering and metalworking,
rather than doom them to ``uneducated'' match girl reputations~\cite{10.2307/3827491}.
However, many such experts are already available on platforms such as Upwork, so training may not directly increase the complexity accessible to crowd work unless it makes common expertise more broadly available.

Will the shift from human managers to Turing-complete algorithms raise the complexity ceiling? 
By the Turing test, the algorithms would be at best indistinguishable from human piecework clerks and foremen.
%At worst, as now, they are far simpler~\cite{uberAlgorithm}.
So in terms of enabling coordination, algorithmic management is unlikely to directly raise the ceiling beyond what piecework could achieve.
However, as a resource constraint, algorithms are a fixed cost and not a per-person cost like human managers.
So in terms of accessibility, algorithms will allow a broader class of organizations and individuals to afford on--demand labor.
This shift may enable complex work that was not cost-effective before to become feasible.

Because algorithms remain far from replicating all of the foremen's responsibilities, most likely is a middle ground in which crowd work re-introduces the human element to management in a more targeted way~(e.g.,~\cite{haas2015argonaut,kulkarni2012mobileworks,crowdguilds}).
This move, however, will require resolving the tension between workers and perilously antagonistic managers, as \citeauthor{10.2307/2118435} suggest, to break a toxic cycle of mistrustful requesters \cite{MaliciousCrowdworkersGadiraju}.
% and develop more considerate platforms as \citeauthor{takingAHITMcInnis} advocate
% \cite{takingAHITMcInnis}.
% \ali{What will happen if we don't do this?
% Maybe this is where I should bring up
% the ``market for lemons'' metaphor and say that
% the market will just continue to decline in quality until
% nobody is willing to rely on it either as a source of data/information (requesters), or
% a means of sustaining oneself financially (workers).}

>>>>

\subsubsection{\implication}
% \topic{The piecework literature gives us a template for pushing the boundaries of complexity in piecework, but
% it also signals some of the ultimate limitations of crowd work and piecework in general.}
% While the threshold preventing task requesters from utilizing piecework
% has dropped thanks to affordances of the Internet, the ceiling on task complexity hasn't moved significantly.
% \msb{is that your prediction? I would argue against the fact that it hasn't moved significantly, crowdforge did far more complex work, as did flash teams and flash orgs}
% If we're to make use of \citeauthor{Brown01041990}'s prescriptions,
% we would benefit from finding ways to decompose varied tasks into homogeneous microtasks. \msb{isn't that what we've been doing all along?}
Technology's ability to support human cognition will enable stronger assumptions about workers' abilities, increasing the complexity of crowd work outcomes.
Just as the shift to expert crowdsourcing increased complexity, so too will workers with better tools increase the set of tasks possible.
Beyond this, further improvements would most likely come from replicating the success of narrowly-slicing education for expert work as \citeauthor{hart2013rise} and \citeauthor{grier2013computers} described in their piecework examples
of human computation \cite{grier2013computers} and drastically reformulating macro--tasks given the constraints of piecework \cite{hart2013rise}.
To some extent, an argument can be made that
MOOCs and other online education resources
provide crowd workers with the resources that they need, but 
it remains to be seen whether that work will be appropriately valued, let alone
properly interpreted by task solicitors
\cite{aguaded2013mooc}.
If we can overcome this obstacle,
we might be able to empower more crowd workers to do complex work such as engineering and metalworking,
rather than doom them to ``uneducated'' match girl reputations~\cite{10.2307/3827491}.
However, many such experts are already available on platforms such as Upwork, so training may not directly increase the complexity accessible to crowd work unless it makes common expertise more broadly available.

Will the shift from human managers to Turing-complete algorithms raise the complexity ceiling? 
By the Turing test, the algorithms would be at best indistinguishable from human piecework clerks and foremen.
%At worst, as now, they are far simpler~\cite{uberAlgorithm}.
So in terms of enabling coordination, algorithmic management is unlikely to directly raise the ceiling beyond what piecework could achieve.
However, as a resource constraint, algorithms are a fixed cost and not a per-person cost like human managers.
So in terms of accessibility, algorithms will allow a broader class of organizations and individuals to afford crowd work.
This shift may enable complex goals that were not cost-effective before to become feasible.
However, because algorithms remain far from replicating all of the foremen's responsibilities, most likely is a middle ground in which crowd work re-introduces the human element to management in a more targeted way~(e.g.,~\cite{haas2015argonaut,kulkarni2012mobileworks,crowdguilds}).
This move will require resolving the tension between workers and perilously antagonistic managers, as \citeauthor{10.2307/2118435} suggest, to break a toxic cycle of mistrustful requesters \cite{MaliciousCrowdworkersGadiraju}.
% and develop more considerate platforms as \citeauthor{takingAHITMcInnis} advocate
% \cite{takingAHITMcInnis}.
% \ali{What will happen if we don't do this?
% Maybe this is where I should bring up
% the ``market for lemons'' metaphor and say that
% the market will just continue to decline in quality until
% nobody is willing to rely on it either as a source of data/information (requesters), or
% a means of sustaining oneself financially (workers).}

### 2016-09-21 drafts/labor/decomposition.tex
looked through complexity

\documentclass[trackingWork]{subfiles}
% \makeatletter
% \def\blx@maxline{77}
% \makeatother
\onlyinsubfile{\usepackage{xr-hyper}
\usepackage{hyperref}
\externaldocument{complexity}
\externaldocument{relationships}
\externaldocument{decomposition}
}
\begin{document}

@@

\topic{A second shift is  
%A number of factors in crowd work are different from piecework, chief among them being 
the relative ease with which the metaphorical ``assembly line'' can be changed.}
% Computers make it possible to switch from one task to another unlike any arbitrary manufacturing factory possibly could;
%modern on--demand workers on AMT and other platforms can more readily do any number of
%different \textit{types} of tasks in the span of just a few minutes
Historical manufacturing equipment was not Turing-complete, and could not quickly be assembled, edited, and redeployed.\msb{cite for historical piecework equipment being a large time + money investment?}
In contrast, today system--designers can share, modify, and instantiate environments
like sites of labor in a few lines of code
\cite{lessig2006code,turkitLittle}.
This opportunity has spurred an entire body of work investigating the effects of
ordering,
pacing,
interruptions, and
other factors in piecework that would have been
all but impossible to manipulate as few as 20 years ago
\cite{dai2015and,Cai:2016:CRI:2858036.2858237,cheng2015break,measuringCrowdsourcingCheng,embracingErrorKrishna}.

@@

\onlyinsubfile{
  \balance{}
  \printbibliography
}

>>>>

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
% \onlyinsubfile{
% \usepackage{xr-hyper}
% \usepackage{hyperref}
% \externaldocument{complexity}
% \externaldocument{relationships}
% % \externaldocument{decomposition}
% }
\begin{document}

@@

\topic{A second shift is  
%A number of factors in crowd work are different from piecework, chief among them being 
the relative ease with which the metaphorical ``assembly line'' can be changed.}
% Computers make it possible to switch from one task to another unlike any arbitrary manufacturing factory possibly could;
%modern on--demand workers on AMT and other platforms can more readily do any number of
%different \textit{types} of tasks in the span of just a few minutes
Historical manufacturing equipment could not quickly be assembled, edited, and redeployed.\msb{cite for historical piecework equipment being a large time + money investment?}
In contrast, today system--designers can share, modify, and instantiate environments
like sites of labor in a few lines of code
\cite{lessig2006code,turkitLittle}.
This opportunity has spurred an entire body of work investigating the effects of
ordering,
pacing,
interruptions, and
other factors in piecework that would have been
all but impossible to manipulate as few as 20 years ago
\cite{dai2015and,Cai:2016:CRI:2858036.2858237,cheng2015break,measuringCrowdsourcingCheng,embracingErrorKrishna}.

@@

% \onlyinsubfile{
%   \balance{}
%   \printbibliography
% }
